
---
title: "I have the best titles"
author: Your name here
subtitle: Subtitle here if desired
---

# Introduction
Historically, hate-groups were prominent in communities with white majority populations with a marginalized racial minority group. (Beck, 2000). Hate groups in the past were more commonly forming in material communities, but now with the rise in Internet Communication Technologies (ICT’s) are fostering hateful communities online.  


# The Big Question

Which material conditions are relevant to producing raciest rhetoric on Twitter? (Income, interracial marriage, employment, education)  What are the demographics of the geographic area surrounding online hate-speech activists, compared to the demographics of hate-groups existing in the material environment?

# Methodology

Here's my first code chunk.
```{r}
Nword <- read.csv(file = "Nword.csv", header = TRUE, stringsAsFactors = FALSE)

NWordHate<-subset(Nword, Hate==1)

NewNword=select(NWordHate, latitude, longitude, Hate)
edit(NewNword)


usa <- map_data("usa")
ggplot() + geom_polygon(data = usa, aes(x=long, y = lat, group = group)) + 
  geom_point(data=NewNword, aes(x=longitude, y=latitude), color="red", size = .2) +
  coord_fixed(1.3)
```

Load any required packages in a code chunk (you may need to install some packages):

```{r, message=F, warning=F}
library(dplyr)
library(ggplot2)
library(tidyverse)

```



```{r, warning=F} 
## define which species to query
sp='Turdus migratorius'

## run the query and convert to data.frame()
d = occ(query=sp, from='ebird',limit = 100) %>% occ2df()
```
This can take a few seconds.

```{r, fig.width=6, fig.height=3, fig.cap="Map illustrating the known occurrence locations"}
# Load coastline
map=map_data("world")

ggplot(d,aes(x=longitude,y=latitude))+
  geom_polygon(aes(x=long,y=lat,group=group),data=map)+
  geom_point(col="red")+
  coord_equal()
```


# Results

Show tables, plots, etc. and describe them.

# Conclusions

What have you learned?  Are there any broader implications?

# References

